---
title: "**Navigational affordances are automatically computed during scene perception**: <br /> Evidence from behavioral change blindness and a computational model of active attention"
title_textsize: "105pt"
author_textcol: "#ffffff"
author_textsize: "75pt"
author:
  - name: Mario Belledonne
    # affil: 1
  - name: Yihan Bao
    # affil: 2
  - name: Ilker Yildirim
  # - affil: 1,2
affiliation:
# - num: 1
  #   address: Department of Psycholgy, Yale University
  # - num: 2
  #   address: Department of Statistics and Data Science, Yale University
affiliation_textcol: "#B3D4E5"
column_numbers: 4
logoright_name: "vss_poster_files/figure-html/VSS_logo.svg"
logoleft_name: "vss_poster_files/figure-html/lab_logo.svg"

output: 
  posterdown::posterdown_html:
    self_contained: false
    
bibliography: main.bib

poster_height: "36in"
poster_width: "82in"
primary_colour: "#153a72ff"
# primary_colour: "#2d6686"
# secondary_colour: "#193b4d"
secondary_colour: "#153a72ff"
accent_colour: "#153a72ff"
# titlebox_bordercol: "#193B4D"
titlebox_bordercol: "#525252fc"
titlebox_borderwidth: "1.0cm"
# accent_colour: "#193b4d"


sectitle_bordercol: "#153a72ff"
sectitle_bgcol: "#80b1d1"
sectitle_borderwidth: "5mm"
# sectitle_bgcol: "#193b4d"
sectitle_textsize: "80pt"

sectitle2_textsize: "70pt"
body_textsize: "65pt"

columnline_width: "0.3cm"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# knitr::opts_knit$set(root.dir = '~/project')


```

<!-- make fonts bigger! -->
# The "Get Me Out of Here!"<br /> Hypothesis

<br />

You are meeting a friend upstairs: 
*What do you see?*

```{r fig1, fig.align = 'center', out.width = "95%", }
knitr::include_graphics("vss_poster_files/figure-html/museum.svg")
```

*Now* imagine that your friend is at the art gallery.


<!-- From this example, it may not surprise you that explicit navigational goals influence -->
<!-- our perception of scenes... -->

<!-- However, we believe  navigating in and out of rooms is -->
<!-- such a core target of scene perception, that our minds sponteously compute  -->
<!-- exit paths. -->

<!-- In this work, we explore signatures of this implicit goal in the selective processing of -->
<!-- scene geometry in indoor scenes similar to one above.  -->

### *Do we automatically process navigational affordances?*

<!-- To evaluated whether... -->

> 1. Humans **spontaneously compute exit paths** when viewing scenes.

> 2. This **implicit goal** induces selective processing of **scene geometry**.

<!-- we employ a change detection paradigm -->

# Change Detection: <br /> Human sensitivity to pathing

## With *no explicit reference to navigation*, subjects simply compared images.

<!-- Changes in these images results from moving a single obstacle in one of two ways.. -->

**Different path trials**:
Scenes had a change in geometry (by moving an <span style="color:blue">
**obstacle** </span>) that impacted the path to the exit. 

```{r path_chng, fig.align = 'center', out.width = "95%", }
knitr::include_graphics("vss_poster_files/figure-html/path_chng.svg")
```

**Same path trials**: Scenes had a change in geometry that did **not** impact 
the path to the exit. 

```{r no_path_chng, fig.align = 'center', out.width = "95%", }
knitr::include_graphics("vss_poster_files/figure-html/no_path_chng.svg")
```

> <u>Each</u> *different path* trial had a geometry-matched *same path* trial 
expect for the position of the exit.


# Humans spontaneoulsy compute navigational affordances


## Comparing detection rate between ***Same*** and ***Different*** path pairs

```{r abs_chng, fig.align = 'center', out.width = "85%"}
knitr::include_graphics("vss_poster_files/figure-html/abs_chng_full.svg")
```

Attention can <span style="color:#00bfc4ff"> **help** </span> or 
<span style="color:#f8766dff"> **hurt** </span>!


```{r help_hurt, fig.align = 'center', out.width = "85%"}
knitr::include_graphics("vss_poster_files/figure-html/help_hurt.svg")
```

Path Effect is nullified by *inverting images*! (p = .89)


<!-- Super excited about behavioral scientist  -->
<!-- What are the computational principles, specifically the processes and representations underlying this phenomena -->

<!-- based on a new way to think about attention (presented last year). and here is how it works -->


# Reverse-engineering selective formation of scene percepts

## Modelling scene perception based on a new a way to think about attention

```{r model, fig.align = 'center', out.width = "95%"}
knitr::include_graphics("vss_poster_files/figure-html/model.svg")
```

# Acknowledgements
<span style="font-size: 55pt">  
Supported by AFOSR FA9550-22-1-0041.
Special thanks to Brian Scholl, Kim Wong, Qi Lin for feedback on experimental design and analysis.
</span>

<!-- ```{r, include=FALSE} -->
<!-- knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), "packages.bib") -->
<!-- ``` -->
